### 2014-08-31 Paper_v1.tex
Updated captions for Fig 1 - 6

\begin{figure}
\centering
\includegraphics[width=1.0\textwidth]{./figs/Figure-2-ControlSchematic.pdf}
\caption{Schematic of the rule based allosteric enzyme activity control laws. }\label{fig-control-schematic}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1.0\textwidth]{./figs/Figure-3-EnzymeKinetics.pdf}
\caption{Kinetics of simple transformations in the presence of activation and inhibition. 
A:The conversion of substrate $S$ to product $P$ by enzyme $E$ was activated by $S$. 
B:The conversion of substrate $S$ to product $P$ by enzyme $E$ was inhibited by inhibitor $I$. 
}\label{fig-kinetics-simulations}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.55\textwidth]{./figs/Figure-4-OnOffSimulations.pdf}
\caption{On/off control simulations for network A and network B for an ensemble of kinetic parameter sets versus time. 
For each case, N = 100 simulations were conducted using kinetic and initial conditions randomly generated from a hypothetical true parameter set. 
The gray area represents $\pm$ one standard deviation surrounding the mean. Control parameters were fixed during the ensemble calculations.}\label{fig-onoff-simulations}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1.0\textwidth]{./figs/Figure-5-ParameterFit.pdf}
\caption{Parameter estimation from synthetic data for the same and mismatched allosteric control logic. }\label{fig-parameter-fit}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{./figs/Figure-7-ControlSearch.pdf}
\caption{Combined control structure and kinetic parameter search results. Think about this ...}\label{fig-control-search}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=1.0\textwidth]{./figs/Figure-2-ControlSchematic.pdf}
\caption{Schematic of rule based allosteric enzyme activity control laws. 
Traditional enzyme kinetic expressions e.g., Michaelis–Menten or multiple saturation kinetics are multiplied by an enzyme activity control variable $0 \leq v_{j} \leq 1 $. 
Control variables are functions of many possible regulatory factors encoded by arbitrary functions of the form $0\leq f_{j}\left(\mathcal{Z}\right)\leq 1$.
At each simulation time step, the $v_{j}$ variables are calculated by evaluating integration rules such as the max or min of the set of factors $f_{1},\hdots$ 
influencing the activity of enzyme $E_{j}$. }\label{fig-control-schematic}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1.0\textwidth]{./figs/Figure-3-EnzymeKinetics.pdf}
\caption{Kinetics of simple transformations in the presence of activation and inhibition. 
\textbf{A}:The conversion of substrate $S$ to product $P$ by enzyme $E$ was activated by $S$. 
For a fixed control gain parameter $k_{control}$, the reaction rate approached a step for increasing control order $N$. 
\textbf{B}:The conversion of substrate $S$ to product $P$ by enzyme $E$ with inhibitor $I$. 
For a fixed control gain parameter $k_{control}$, the reaction rate approximated non-competitive inhibition for increasing control order $N$. 
}\label{fig-kinetics-simulations}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.50\textwidth]{./figs/Figure-4-OnOffSimulations.pdf}
\caption{ON/OFF control simulations for network A and network B for an ensemble of kinetic parameter sets versus time (N = 100). 
For each case, N = 100 simulations were conducted using kinetic and initial conditions generated randomly from a hypothetical true parameter set. 
The gray area represents $\pm$ one standard deviation surrounding the mean. 
Control parameters were fixed during the ensemble calculations.
\textbf{A}: End-product P$_{1}$ abundance versus time for Network A. 
The abundance of P$_{1}$ decreased with end-product inhibition of $E_{1}$ activity (Control-ON) versus the no inhibition case (Control-OFF). 
\textbf{B}: End-product P$_{2}$ abundance versus time for Network B. Inhibition of branch point $E_{6}$ by end-product P$_{1}$ decreased P$_{2}$ abundance (Control-ON) versus the
no inhibition case (Control-OFF).
\textbf{C}: End-product P$_{1}$ abundance versus time for Network A. 
Inhibition of branch point $E_{6}$ by end-product P$_{1}$ decreased P$_{1}$ abundance (Control-ON) versus the no inhibition case (Control-OFF).
}\label{fig-onoff-simulations}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1.0\textwidth]{./figs/Figure-5-ParameterFit.pdf}
\caption{Parameter estimation from synthetic data for the same and mismatched allosteric control logic using particle swarm optimization (PSO). 
Synthetic experimental data was generated from a hypothetical parameter set using Network A, 
where substrate $S$, end-product P$_{1}$ and intermediate M$_5$ were sampled approximately every 20 minutes. 
For cases $\textbf{A,B}$ 20 particles were initialized with randomized parameters and allowed to search for 300 iterations. 
\textbf{A,B}: PSO estimated an ensemble of parameters sets (N = 20) consistent with the synthetic experimental data assuming the correct
enzymatic and control connectivity starting from randomized initial parameters.
\textbf{C,D}: In the presence of control mismatch (Network B control policy simulated with Network A kinetic parameters) 
the ensemble of models did not describe the synthetic data. 
}\label{fig-parameter-fit}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{./figs/Figure-7-ControlSearch.pdf}
\caption{Combined control structure and kinetic parameter search results. Think about this ...}\label{fig-control-search}
\end{figure}
